---
title: "ProgammingAssignment2"
author: "Edwin Cheteni"
date: "Saturday, July 14, 2018"
output: html_document
---
Matrix inversion is usually a costly computation and there may be some benefit to caching the inverse of a matrix rather than compute it repeatedly. The following two functions are used to cache the inverse of a matrix.

## makeCacheMatrix creates a list containing a function to
1. set the value of the matrix
2. get the value of the matrix
3. set the value of inverse of the matrix
4. get the value of inverse of the matrix
```{r}
makeCacheMatrix <- function(x = matrix()) {
  inv <- NULL
  set <- function(y) {
    x <<- y
    inv <<- NULL
  }
  get <- function() x
  setinverse <- function(inverse) inv <<- inverse
  getinverse <- function() inv
  list(set=set, get=get, setinverse=setinverse, getinverse=getinverse)
}
```
cacheSolve retrieve the inverse of a matric returned by makeCacheMatrix above from the cache that has already been calculated.
```{r}
cacheSolve <- function(x, ...) {
  inv <- x$getinverse()
  if(!is.null(inv)) {
    message("getting cached data.")
    return(inv)
  }
  data <- x$get()
  inv <- solve(data)
  x$setinverse(inv)
  inv
}
```
Sample run:
```{r}
x = rbind(c(3, -4), c(-8, 2))
m = makeCacheMatrix(x)
m$get()
cacheSolve(m)
```